Chr2 hotspot analyses

### 2019-07-08 analysis/paper/Chr11.Rmd
updated Rmd files for each hotspot

---
title: "Chr2 hotspot preliminary analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 2
run_num <- 9941
hot_mid <- 165.5
```

@@

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()

for (j in 1:nlocal){
  foo <- list()
  for (i in 1:nnonlocal){
    foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             )
  }
  out[[j]] <- foo
}
```

@@

```{r read_pleio_results}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
dir(results_dir) -> fns
mylist <- list()
for (i in 1:length(fns)){
  mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
  as_tibble() %>%
  mutate(filename = fns[i]) %>%
  mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
  filter(lod == max(lod), trace == "profile1") %>%
  select(local_gene_id, nonlocal_gene_id, lod, filename)
}
```

@@

```{r plot_all}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1)
plotly::ggplotly(p)

@@

```{r, plotly_by_local, fig.height=ceiling(nlocal / 2), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) + theme(legend.position = "none")
plotly::ggplotly(p)
```

```{r, plotly_by_nonlocal, fig.height=ceiling(nnonlocal / 4), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ nonlocal_symbol, ncol = 4, nrow = ceiling(nnonlocal / 4)) + theme(legend.position = "none")
plotly::ggplotly(p)
```

@@

```{r heat_pleio_stats}
foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
mylist_local <- list()
for (i in 1:length(fns)){
  mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
  as_tibble() %>%
  mutate(filename = fns[i]) %>%
  mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
  filter(lod == max(lod), trace == "profile1") %>%
  select(gene1_id, gene2_id, lod, filename)
}
```

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
mylist_nonlocal <- list()
for (i in 1:length(fns)){
  mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
  as_tibble() %>%
  mutate(filename = fns[i]) %>%
  mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], 
         gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
  filter(lod == max(lod), trace == "profile1") %>%
  select(gene1_id, gene2_id, lod, filename)
}
```

@@

```{r rafalib_plot}
pleio_results_mat %>%
  dist() %>%
  hclust() %>% 
  rafalib::myplclust(
                     lab.col = 1 + (rownames(pleio_results_mat) %in% local_annot3$annot.id), cex = 0.1
                     )
```

@@

## Clustering of the rectangular nlocal by nnonlocal matrix

@@

```{r, load_colors}
library(RColorBrewer) 
library(genefilter)
library(gplots)
```

@@

```{r threshold_clust}
med_thresh <- 2
foomat <- foo %>%
  select(1, 2, 4) %>% # choose lod_diff_proportion as stat of interest
  tibble_to_matrix()
  apply(FUN = function(x) x <= med_thresh, X = foomat, MARGIN = 2) %>%
    d3heatmap()
```

```{r}
foo %>%
  select(1, 2, 4) %>% # choose lod_diff_proportion as stat of interest
  tibble_to_matrix() %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

@@

## kmeans

```{r kmeans}
set.seed(01-28-1978)
# replace NA with zeros
pleio_resd0 <- apply(FUN = function(x){x[is.na(x)] <- 0; return(x)}, X = pleio_results_mat, MARGIN = 2)
#km <- kmeans(t(e[1:2,]), centers=7)
#names(km)

@@

>>>>

---
title: "Chr11 hotspot analyses"
author: "Frederick Boehm"
date: "July 8, 2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 11
run_num <- 9921
hot_mid <- 71
keller_mediator <- "Sat2"
library(hotspots)
```

@@

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()
medfile <- paste0("_cache/Chr", hot_chr, "_mediations.rds")
if (!file.exists(medfile)){
  for (j in 1:nlocal){
  foo <- list()
  for (i in 1:nnonlocal){
    foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             )
  }
  out[[j]] <- foo
}
saveRDS(out, medfile)
} else {out <- readRDS(medfile)}
```

@@

```{r read_pleio_results}
pleio_file <- paste0("_cache/Chr", hot_chr, "_pleio.rds")
if (file.exists(pleio_file)) {mylist <- readRDS(pleio_file)} else {
  results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
  dir(results_dir) -> fns
  mylist <- list()
  for (i in 1:length(fns)){
    mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(local_gene_id, nonlocal_gene_id, lod, filename)
  }
  saveRDS(mylist, pleio_file)
}
```

@@

```{r plot_all}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.05)
plotly::ggplotly(p)

@@

```{r, plotly_by_local, fig.height=ceiling(nlocal / 2), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) + theme(legend.position = "none")
#plotly::ggplotly(p)
```

```{r, plotly_by_nonlocal, fig.height=ceiling(nnonlocal / 4), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ nonlocal_symbol, ncol = 4, nrow = ceiling(nnonlocal / 4)) + theme(legend.position = "none")
#plotly::ggplotly(p)
```

@@

```{r heat_pleio_stats, fig.height=4, fig.width = 6}
foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
pleio_file_local <- paste0("_cache/Chr", hot_chr, "_pleio_local.rds")
if (file.exists(pleio_file_local)) {mylist_local <- readRDS(pleio_file_local)} else {
  mylist_local <- list()
  for (i in 1:length(fns)){
    mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_local, pleio_file_local)
}

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
pleio_file_nonlocal <- paste0("_cache/Chr", hot_chr, "_pleio_nonlocal.rds")
if (file.exists(pleio_file_nonlocal)) {mylist_nonlocal <- readRDS(pleio_file_nonlocal)} else {
  mylist_nonlocal <- list()
  for (i in 1:length(fns)){
    mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], 
           gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_nonlocal, pleio_file_nonlocal)
}
```

@@

```{r rafalib_plot}
pleio_results_mat %>%
  dist() %>%
  hclust() %>% 
  rafalib::myplclust(cex = 0.1
                     )
```

```{r rafalib_plot2}
bar <- foo %>%
  filter(local_symbol == keller_mediator) # gene symbol from the keller supplementary table

pleio_hc <- foo %>%
  tibble_to_matrix() %>%
  t() %>%
  dist() %>%
  hclust()

rafalib::myplclust(pleio_hc,
                     lab.col = 1+ round(bar$pleiotropy_lod[match(x = bar$nonlocal_symbol, table = pleio_hc$labels)]),
                     cex = 0.3
                     )
```

```{r}
rafalib::myplclust(pleio_hc,
                   lab.col = 1 + (bar$lod_diff[match(x = bar$nonlocal_symbol,
                                                     table = pleio_hc$labels)] >
                                    mediation_threshold),
                     cex = 0.3
                     )

```{r}
library(RColorBrewer) 
library(genefilter)
library(gplots) ##Available from CRAN
cols <- palette(RColorBrewer::brewer.pal(8, "Dark2"))
#head(cbind(colnames(e),cols))
```

```{r heatmap.2}
pleio_mat <- foo %>%
  tibble_to_matrix() %>%
  t()
ld <- bar$lod_diff
idx1 <- match(x = bar$nonlocal_symbol, table = rownames(pleio_mat))
idx <- 1 + floor((ld * (ld > 0))[idx1])
cols[idx] -> indexed_colors
ic2 <- 1 + (ld[idx1] > mediation_threshold)
#indexed_colors[is.na(indexed_colors)] <- cols[8]
gplots::heatmap.2(pleio_mat, 
                  trace="none", 
                  #RowSideColors = indexed_colors, 
                  RowSideColors = c("red", "green")[ic2],
                  col=hmcol,
                  cexRow = 0.5,
                  cexCol = 0.5
                  )
```

```{r}
d3heatmap::d3heatmap(t(pleio_mat) <= 4, cexRow = 0.2, cexCol = 0.3)
```

```{r}
gplots::heatmap.2(t(pleio_mat), 
                  trace="none", 
                  #RowSideColors = indexed_colors, 
                  ColSideColors = c("red", "green")[ic2],
                  col=hmcol,
                  cexRow = 0.5,
                  cexCol = 0.5
                  )

## Cutting the dendrogram

@@

## Clustering of the rectangular nlocal by nnonlocal matrix of pleiotropy results

@@

@@

```{r threshold_clust}
med_thresh <- 2
foomat <- foo %>%
  select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix()
  apply(FUN = function(x) x <= med_thresh, X = foomat, MARGIN = 2) %>%
    d3heatmap()
```

```{r}
foo %>%
  select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix() %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

@@

Consider, also, truncating negative values at zero for the mediation analyses.

@@

## Biclustering with `biclust` R package

```{r}
library(biclust)
```

```{r}
bccc_out<- biclust(pleio_mat, method = BCCC())
c1 <- bicluster(pleio_mat, bccc_out, number = 1)
d3heatmap(c1$Bicluster1, "none", Rowv = FALSE, cexRow = 0.3, cexCol = 0.3)
```

```{r}
d3heatmap(c1$Bicluster1, cexRow = 0.3, cexCol = 0.3)

```{r}
bccc_out2 <- biclust(pleio_mat > pleiotropy_threshold, method = BCCC())
bccc_out2
```

```{r}
biclust(pleio_mat > pleiotropy_threshold, method = BCBimax())
```

## Clustering only those nonlocal traits that aren't mediated by `r keller_mediator`

Another approach is to cluster only those traits that aren't 
mediated by `r keller_mediator`. For now, let's use the lod difference threshold 
1.5 to define mediation.

```{r}
# subset to get nonlocals that aren't mediated by Hnf4a
# first, get symbols for nonlocals that aren't mediated by Hnf4a
pmat <- bar %>%
  filter(lod_diff <= mediation_threshold) %>%
  dplyr::select(nonlocal_symbol) %>%
  left_join(foo) %>%
  tibble_to_matrix()
dim(pmat)
```

```{r d3heat}
d3heatmap(pmat, cexRow = 0.3, cexCol = 0.3)
```
```{r heat_binary}
hc1 <- hclust(dist(pmat))
plot(hc1, cex = 0.3)
hc2 <- hclust(dist(t(pmat)))
plot(hc2, cex = 0.3)
pmat %>%
  dist() %>%
  hclust()

```{r d3heat_logical}
d3heatmap(pmat > pleiotropy_threshold, cexRow = 0.3, cexCol = 0.3)
```

```{r}
dim(pmat)
length(hc1$order)
d3heatmap(pmat[hc1$order, hc2$order] > pleiotropy_threshold, 
          Rowv = FALSE, 
          Colv = FALSE, 
          cexRow = 0.3, 
          cexCol = 0.3)
d3heatmap(pmat[hc1$order, hc2$order], 
          Rowv = FALSE, 
          Colv = FALSE, 
          cexRow = 0.3, 
          cexCol = 0.3)

## Local-local pleiotropy test results

```{r local-local-pleio}
local_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap()
```

## Nonlocal-nonlocal pleiotropy test results

```{r nonlocal-nonlocal-pleio}
nonlocal_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```

### 2019-07-08 analysis/paper/Chr13.Rmd
updated Rmd files for each hotspot

---
title: "Chr11 hotspot analyses"
author: "Frederick Boehm"
date: "July 8, 2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 11
run_num <- 9921
hot_mid <- 71
keller_mediator <- "Sat2"
library(hotspots)
```

>>>>

---
title: "Chr13 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 13
run_num <- 9931
hot_mid <- 112.5
keller_mediator <- "Il6st"
library(hotspots)
```

### 2019-07-08 analysis/paper/Chr2.Rmd
updated Rmd files for each hotspot

---
title: "Chr13 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 13
run_num <- 9931
hot_mid <- 112.5
keller_mediator <- "Il6st"
library(hotspots)
```

@@

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()
medfile <- paste0("_cache/Chr", hot_chr, "_mediations.rds")
if (!file.exists(medfile)){
  for (j in 1:nlocal){
  foo <- list()
  for (i in 1:nnonlocal){
    foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             )
  }
  out[[j]] <- foo
}
saveRDS(out, medfile)
} else {out <- readRDS(medfile)}
```

@@

```{r read_pleio_results}
pleio_file <- paste0("_cache/Chr", hot_chr, "_pleio.rds")
if (file.exists(pleio_file)) {mylist <- readRDS(pleio_file)} else {
  results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
  dir(results_dir) -> fns
  mylist <- list()
  for (i in 1:length(fns)){
    mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(local_gene_id, nonlocal_gene_id, lod, filename)
  }
  saveRDS(mylist, pleio_file)
}
```

@@

```{r heat_pleio_stats, fig.height=4, fig.width = 6}
foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
pleio_file_local <- paste0("_cache/Chr", hot_chr, "_pleio_local.rds")
if (file.exists(pleio_file_local)) {mylist_local <- readRDS(pleio_file_local)} else {
  mylist_local <- list()
  for (i in 1:length(fns)){
    mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_local, pleio_file_local)
}

@@

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
pleio_file_nonlocal <- paste0("_cache/Chr", hot_chr, "_pleio_nonlocal.rds")
if (file.exists(pleio_file_nonlocal)) {mylist_nonlocal <- readRDS(pleio_file_nonlocal)} else {
  mylist_nonlocal <- list()
  for (i in 1:length(fns)){
    mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], 
           gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_nonlocal, pleio_file_nonlocal)
}
```

@@

```{r rafalib_plot2}
bar <- foo %>%
  filter(local_symbol == keller_mediator) # gene symbol from the keller supplementary table

@@

```{r}
d3heatmap::d3heatmap(t(pleio_mat) <= 4, cexRow = 0.2, cexCol = 0.3)
```

@@

## Clustering only those nonlocal traits that aren't mediated by `r keller_mediator`

Another approach is to cluster only those traits that aren't 
mediated by `r keller_mediator`. For now, let's use the lod difference threshold 
1.5 to define mediation.

>>>>

---
title: "Chr2 hotspot analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 2
run_num <- 9941
hot_mid <- 165.5
library(hotspots)
library(igraph)
library(d3heatmap)
```

@@

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()
medfile <- "_cache/Chr2_mediations.rds"
if (!file.exists(medfile)){
  for (j in 1:nlocal){
  foo <- list()
  for (i in 1:nnonlocal){
    foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             )
  }
  out[[j]] <- foo
}
saveRDS(out, medfile)
} else {out <- readRDS(medfile)}
```

@@

```{r read_pleio_results}
pleio_file <- "_cache/Chr2_pleio.rds"
if (file.exists(pleio_file)) {mylist <- readRDS(pleio_file)} else {
  results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
  dir(results_dir) -> fns
  mylist <- list()
  for (i in 1:length(fns)){
    mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(local_gene_id, nonlocal_gene_id, lod, filename)
  }
  saveRDS(mylist, pleio_file)
}
```

@@

```{r heat_pleio_stats}
foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
pleio_file_local <- "_cache/Chr2_pleio_local.rds"
if (file.exists(pleio_file_local)) {mylist_local <- readRDS(pleio_file_local)} else {
  mylist_local <- list()
  for (i in 1:length(fns)){
    mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_local, pleio_file_local)
}

@@

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
pleio_file_nonlocal <- "_cache/Chr2_pleio_nonlocal.rds"
if (file.exists(pleio_file_nonlocal)) {mylist_nonlocal <- readRDS(pleio_file_nonlocal)} else {
  mylist_nonlocal <- list()
  for (i in 1:length(fns)){
    mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], 
           gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_nonlocal, pleio_file_nonlocal)
}
```

@@

```{r rafalib_plot2}
bar <- foo %>%
  filter(local_symbol == "Hnf4a")

@@

```{r}
d3heatmap(t(pleio_mat) <= 4, cexRow = 0.2, cexCol = 0.3)
```

@@

## Clustering only those nonlocal traits that aren't mediated by Hnf4a

Another approach is to cluster only those traits that aren't 
mediated by Hnf4a. For now, let's use the lod difference threshold 
1.5 to define mediation.
